---
title: "Week 9 Assignment - Web APIs"
author: "Puja Roy"
date: "3/24/24"
output: openintro::lab_report
---

### Objective

The New York Times web site provides a rich set of APIs, as described here: https://developer.nytimes.com/apis

You’ll need to start by signing up for an API key.

The main objective is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame.

I chose to retrieve data from the NY Times Books API. This API retrieves NY Times book reviews and obtains data from all best-seller lists.

### Load Libraries
```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(httr)
library(jsonlite)
```


### Set API Key
```{r echo=FALSE}
# Set your API key
api_key <- "oUThOnq4f0QQvESBUQiMfvtmBJjA33i4"
```

### Define API Endpoint & Set Query Parameters
```{r}
# Define the API endpoint
base_url <- "https://api.nytimes.com/svc/books/v3/reviews.json"

# Set query parameters
params1 <- list(author = "Rachel DeLoache Williams", "api-key" = api_key)
params2 <- list(author = "Stephen King", "api-key" = api_key)
params3 <- list(author = "Toni Morrison", "api-key" = api_key)
```

### Make GET request to the NY Times Book API
```{r}
# Make GET request to the API
response <- GET(url = base_url, query = params1)

# Check if request was successful
if (status_code(response) == 200) {
  # Parse JSON response
  json_data <- content(response, as = "text", encoding = "UTF-8")
  
  # Convert JSON to DataFrame
  df <- jsonlite::fromJSON(json_data)$results
  
  # Display the DataFrame
  print(df)
} else {
  # Print error message with status code
  print(paste("Error:", status_code(response), "- Unable to retrieve data from the API."))
  
  # Print detailed error message
  print(content(response, as = "text"))
}
```

```{r}
# Make GET request to the API
response <- GET(url = base_url, query = params2)

# Check if request was successful
if (status_code(response) == 200) {
  # Parse JSON response
  json_data <- content(response, as = "text", encoding = "UTF-8")
  
  # Convert JSON to DataFrame
  df <- jsonlite::fromJSON(json_data)$results
  
  # Display the DataFrame
  print(df)
} else {
  # Print error message with status code
  print(paste("Error:", status_code(response), "- Unable to retrieve data from the API."))
  
  # Print detailed error message
  print(content(response, as = "text"))
}
```

```{r}
# Make GET request to the API
response <- GET(url = base_url, query = params3)

# Check if request was successful
if (status_code(response) == 200) {
  # Parse JSON response
  json_data <- content(response, as = "text", encoding = "UTF-8")
  
  # Convert JSON to DataFrame
  df <- jsonlite::fromJSON(json_data)$results
  
  # Display the DataFrame
  print(df)
} else {
  # Print error message with status code
  print(paste("Error:", status_code(response), "- Unable to retrieve data from the API."))
  
  # Print detailed error message
  print(content(response, as = "text"))
}
```

...

